Reconstructing Propositional Proofs in Type Theory

### 2017-10-24 paper/sections/introduction.tex
[ paper ] some text added.

disciplina
en el tiempo
hilighting an import

The main challenge faced of reconstrucing proofs

the main disadavantage of X

One of the main obstacles to reconstruct proofs generated by
automatic provers consists of ...

However,

The performance of X is limited by ...

synopsys

Previous studies have reported proof-reconstruction for

Existing research recognizes the critical role by ...

What we known about X is largely based on ....

Few published studied have examined the role of

focus on a full description of the inference rules in the ATP logic.

No previous studies has given sufficient considerations to ...

This paper describes the design and implementation of X...

This study provides new insights into the automatic reasoning of \Metis prover.
Understanding the link between the ATP and ITP will help xxxx

The reader should bear in mind that the study is based on
reverse engineering.

DECIR QUE ES NOVEDOSO EN AGDA Y Q NO ESTA HECHO EN TEORIA DE TIPOS
SYNTATICA VS SEMANTICA.
APPLICACIONES

@@

The recontruction of  proof can play an important role in addressing a issue
of ...
Moreover, verification is fast becoming a key instrument in automatic reasoning.

The type theory provides a useful account of how ...

No previous study has investigated to reconstruct proofs using a syntactical approach
in \Agda for any \ATPs.

>>>>

% During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems. One of the major achievements of this field are the automatic
% theorem provers (henceforth ATPs).

% At the beginning in its development, the main goal was prove automatically
% problems in different logics (\eg, first-order logic, high-order logic).
% Nowadays, they continuing extending its support, performance and precision
% in their deductive methods. To guarantee the validity of their methods,
% many ATPs has been opted to include proofs in their output.
% Nevertheless, it has been argued that some of their deductions are not
% valid even in delivering a proof. One of the reason to say that is
% the discover of bugs in ATPs that outputs unsound proofs.

% This problem to verify proofs delivered by ATPs is a non-trivial task
% and involves an in-depth understanding of the algorithms in the \ATP.

% The proof-reconstruction problem aim to solve this issue.
% One way to address this problem is using another major system in this field, the proof assistants.

% A proof-reconstruction tool using this approach will try to verify the proof delivered by the ATP using the proof assistant.

% In this paper, we purpose one of such proof-reconstruction tools.
% Our approach describes the design and implementation to reconstruct
% proofs of the \Metis prover into a proof assistant for type theory like
% \Agda. We use type theory to guarantee that proofs of the \ATP are valid.

% To begin with the proof-reconstruction, it is
% necessary to have a proof from the \ATP in a consistent
% format, that is, a full script describing step-by-step
% with exhaustive details and without ambiguities, the derivation to
% get the that proof. But this is a strong requirement and its the main obstacle we found with \Metis proofs.
% The reader should bear in mind that the study is based on
% reverse engineering about \Metis.

% The main disadvantage of X

% One of the main obstacles to reconstruct proof generated by this tools
% are their

% One of the main obstacles to reconstruct proofs generated by
% automatic provers consists of ...

% However,

% The performance of X is limited by ...

% synopsys

% Previous studies have reported proof-reconstruction for

% Existing research recognizes the critical role by ...

% What we known about X is largely based on ....

% Few published studied have examined the role of

% focus on a full description of the inference rules in the ATP logic.

% No previous studies has given sufficient considerations to ...

% This paper describes the design and implementation of X...

% This study provides new insights into the automatic reasoning of \Metis prover.
% Understanding the link between the ATP and ITP will help xxxx

% DECIR QUE ES NOVEDOSO EN AGDA Y Q NO ESTA HECHO EN TEORIA DE TIPOS
% SYNTATICA VS SEMANTICA.
% APPLICACIONES

@@

% The recontruction of  proof can play an important role in addressing a issue
% of ...
% Moreover, verification is fast becoming a key instrument in automatic reasoning.

% The type theory provides a useful account of how ...

% No previous study has investigated to reconstruct proofs using a syntactical approach
% in \Agda for any \ATPs.
